A Comparision of Lattice Boltzmann Method Collision Operators for Accuracy, Stability and Efficiency in Simulating Non-Newtonian Flows

### 2015-12-10 main.tex
started writing motivation for non-Newtonian flows

\begin{itemize}
	\item Motivation for non-Newtonian flows
	\item Lattice Boltzmann Method is good for non-Newtonian flow because the collision operator is entirely local to a node.
	\item Parallelability, simplicity, etc. Allows the non-linear constitutive relationship to be solved in parallel.
	\item Lattice Boltzmann Method can be unstable sometimes :(.
	\item Literature review
	\begin{itemize}
		\item history of collision operators: BGK, MRT, etc.
		\item stability analysis
		\item methods of enhancing stability
		\item non-Newtonian flow studies
	\end{itemize}
\end{itemize}

@@

@@

>>>>

\begin{itemize}
	\item Motivation for non-Newtonian flows
	\item Lattice Boltzmann Method is good for non-Newtonian flow because the collision operator is entirely local to a node.
	\item Parallelability, simplicity, etc. Allows the non-linear constitutive relationship to be solved in parallel.
	\item Lattice Boltzmann Method can be unstable sometimes :(.
	\item Literature review
	\begin{itemize}
		\item non-Newtonian flow studies
		\item history of collision operators: BGK, MRT, etc.
		\item stability analysis
		\item methods of enhancing stability
	\end{itemize}
\end{itemize}

@@

There are a number of non-Newtonian flows in engineering applications.
Cement slurries and concretes are best modeled as non-Newtonian fluids because they typically have a non-linear relationship between strain rate and shear stress.
In particular, cement slurries and concretes can be categorized as yield stress fluids. 
Yield stress fluids do not flow until a threshold value of stress, refered to as its yield stress, is exceeded.
Understanding the flow of cement slurries and concretes is important because they are used in the cementing of oil and gas wellbores, in construction, and blah blah blah.
If the cement job for an oil and gas wellbore is not completed successfully then gasses and fluids can leak through the wellbore to contaminate ground water or the atmosphere ~\cite{grasinger2015simulation}.
The goal of understanding cement slurry and concrete flows during construction is to understand how construction forms can be completely filled as voids can lead to structural deficiencies ~\cite{RARR}.
There are probably some other non-Newtonian form filling problems that are super important such as molten metal and plastics filling molds.

@@

\subsection{Lid-driven Flow}
